A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2020-03-27 paper/paper - revision.Rnw
Update beginning of methods and defend choice of online retailer images

\section{Materials and Methods}
%\fix{We may want to mention some of the methods in the introduction for continuity sake...
Ultimately, most pattern evidence is stored in photographic form; as a result, we must use image analysis methods to create numerical features from the original visual record. There are a number of methods that may be employed to identify shapes and features in an image, such as Fourier-Mellin transforms, Hough transformations \citep{ballardGeneralizingHoughTransform1981} and other low-level feature extraction methods aimed at detecting specific shapes, such as edges, corners, blobs, or ridges \citep[Ch 15]{machineVision}. While these methods are useful in identifying these specific features at a low level, they only identify features on a very small scale; as a result, they cannot reliably identify large geometric shapes like those that may be found in a high resolution outsole image.

@@

>>>>

\section{Materials and Methods}

Ultimately, \mt{images collected from a footwear scanner (as described in the previous section) would be} stored in photographic form; as a result, we must use image analysis methods to create numerical features from the original visual record. There are a number of methods that may be employed to identify shapes and features in an image, such as Fourier-Mellin transforms, Hough transformations \citep{ballardGeneralizingHoughTransform1981} and other low-level feature extraction methods aimed at detecting specific shapes, such as edges, corners, blobs, or ridges \citep[Ch 15]{machineVision}. While these methods are useful in identifying these specific features at a low level, they only identify features on a very small scale; as a result, they cannot reliably identify large geometric shapes like those that may be found in a high resolution outsole image.

@@

\fix{Rough idea: A reasonable criticism of this approach is that images from online retailers are of much higher quality than would be expected from the sidewalk scanner proposed earlier in this paper. This critique is especially fair considering that CNNs, and neural networks in general, have been shown to perform poorly on test data when it does not resemble the training data (find citation). However, this research is so new that we need to start somewhere. Once this work shows that CNNs can sufficiently distinguish outsole patterns/features, we can justify the effort to modify this approach for real/degraded images.}
